\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-30 paper/mswp2012-proposal.tex
fixed some spelling mistakes

Analyzing these current systems you can find two strategies, on one hand the gamification of healthcare (see \ref{sect:star:gamification}) and on the other hand a combination of helathcare and social engineering with special plattforms.

@@

\paragraph{Social aspects:} The next step was to add social features to their plattforms to make this service more intersting for their users. They introduced a route-sharing feature, which makes it possible to find interesting routes near you posted by other runners. To get in contact with these people they introduced the so called Street Team to see the activities from your friends and match against each other, a simple way to gamify your daily workout.

@@

\subsubsection{Similar Plattforms}
\label{sect:star:competitors}
There are several other plattforms tracking your sport activities, a lot of them do not offer that many features as RunKeeper does, do not have that many users, or do not follow such an intense social approach.

@@

	One big advantage is the use of Xboxs Kinect which not only combine these two plattforms but also combine the two strategies of gamification and socialisation. \\
	\item \textbf{Other plattforms introduced by several sport equipment manufactors:} Other manufactors like Polar also introduced their own plattforms but have problems to reach a big user-base. They tried to jump on this movement made by plattforms like RunKeeper or Runtastic, but couldn't get that much success with their systems, although they have a lot of success with their equipment.
\end{itemize}

@@

\subsubsection{Literature Research LR1}
\label{sect:workplan:phase1:lr1}
\textbf{Dependencies:} None\\
\textbf{Description:} Find and describe existing Systems and emphasis their approach.
Analyze the user-interfaces and the provided interaction with the system. Establish the functionality and their business model.\\
\textbf{Responsible person(s):} Research Group\\
\textbf{Goal(s) and expected Results:} Information about current systems, their feature set and user-interface\\

\subsubsection{Empirical Study ES1}
\label{sect:workplan:phase1:es1}
\textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
\textbf{Description:} Create questionary for users, to get information about their thoughts about the systems discovered in \ref{sect:workplan:phase1:lr1}. They should evaluate these results and discover issues with their User-Interface and functionality and also mention their needs regarding these two aspects.\\
The users current situation regarding the usage or the willingness to use of current systems are also parts to work out. \\
\textbf{Responsible person(s):} Research Group, Alpha-User \\
\textbf{Goal(s) and expected Results:} Knowledge about the user needs.\\

@@

\subsubsection{Prototyping P1}
\label{sect:workplan:phase2:p1}
\textbf{Dependencies:} RF2 \ref{sect:workplan:phase1:rf2}\\
\textbf{Description:} Create first version of horizontal prototype by creating the user-interface. Every part of the system should be covered.\\
\textbf{Responsible person(s):} Dev-Team\\
\textbf{Goal(s) and expected Results:} first version of prototype\\

\subsubsection{Evaluation and Redesign ER1}
\label{sect:workplan:phase2:er1}
\textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
\textbf{Description:} The Alpha-Users should evaluate the prototype (interface and interaction) and redesign it by taking care of their input. This step should be repeated several times until there is no more additional useful feedback from the user-group.\\
\textbf{Responsible person(s):} Research-Group, Alpha-Users, Dev-Team\\
\textbf{Goal(s) and expected Results:} Information about necessary changes and redesigned prototype (Version 0.5, Milestone M2)\\

\subsubsection{Prototyping P2}
\label{sect:workplan:phase2:p2}
\textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
\textbf{Description:} Extend the existing prototype by adding functionality and implement the features.\\
\textbf{Responsible person(s):} Dev-Team\\
\textbf{Goal(s) and expected Results:} Prototype with all features\\

\pagebreak
\subsubsection{Evaluierung und Redesign ER2}
\label{sect:workplan:phase2:er2}
\textbf{Dependencies:} P2 \ref{sect:workplan:phase2:p2}, ER2 \ref{sect:workplan:phase2:er2}\\
\textbf{Description:} The new prototype should be reevaluated by the Alpha-Users and also from the Dev-Team (including Security and Quality Specialists). This step covers not only the interface and interaction, but also the quality and security of the product. The knowledge should be used to redesign the prototype and this step should be repeated several times. After a number of iterations the status of the web application should be switched to Beta and Beta-Users will be able to sign in and use the systems. After the last iteration the status should be switched to Release.\\
\textbf{Responsible person(s):} Alpha-Users, Beta-Users, Strategy Team, Dev-Team\\
\textbf{Goal(s) and expected Results:} Released web application (Milestone M3)\\

@@

\subsubsection{Empirical Studie ES3}
\label{sect:workplan:phase3:es3}
\textbf{Dependencies:} LR2 \ref{sect:workplan:phase3:lr2}\\
\textbf{Description:} Establish user needs regarding an mobile app and get infos about expectations of such an app \\
\textbf{Responsible person(s):} Research Team, Users\\
\textbf{Goal(s) and expected Results:} User needs regarding an mobile app\\

@@

\subsubsection{Prototyping P3}
\label{sect:workplan:phase3:p3}
\textbf{Dependencies:} ES3 \ref{sect:workplan:phase3:es3}\\
\textbf{Description:} Implement mobile version of the system with prototyping\\
\textbf{Responsible person(s):} Dev-Team\\
\textbf{Goal(s) and expected Results:} Mobile clients\\

\subsubsection{Empirical Studie ES4}
\label{sect:workplan:phase3:es4}
\textbf{Dependencies:} None\\
\textbf{Description:} Establish if and which social health communities (e.g. tracking plattforms) our users are using and find out how to integrate these partner into the system. \\
\textbf{Responsible person(s):} Research Team, Users\\
\textbf{Goal(s) and expected Results:} Possible new partners (3rd party services)\\

>>>>

Analyzing these current systems you can find two strategies, on one hand the gamification of healthcare (see \ref{sect:star:gamification}) and on the other hand a combination of helathcare and social engineering with special platforms.

@@

\paragraph{Social aspects:} The next step was to add social features to their platforms to make this service more intersting for their users. They introduced a route-sharing feature, which makes it possible to find interesting routes near you posted by other runners. To get in contact with these people they introduced the so called Street Team to see the activities from your friends and match against each other, a simple way to gamify your daily workout.

@@

\subsubsection{Similar Platforms}
\label{sect:star:competitors}
There are several other platforms tracking your sport activities, a lot of them do not offer that many features as RunKeeper does, do not have that many users, or do not follow such an intense social approach.

@@

	One big advantage is the use of Xboxs Kinect which not only combine these two platforms but also combine the two strategies of gamification and socialisation. \\
	\item \textbf{Other platforms introduced by several sport equipment manufactors:} Other manufactors like Polar also introduced their own platforms but have problems to reach a big user-base. They tried to jump on this movement made by platforms like RunKeeper or Runtastic, but couldn't get that much success with their systems, although they have a lot of success with their equipment.
\end{itemize}

@@

\subsubsection{Literature Research LR1}
\label{sect:workplan:phase1:lr1}
\textbf{Dependencies:} None\\
\textbf{Description:} Find and describe existing systems and emphasis their approach.
Analyze the user-interfaces and the provided interaction with the system. Establish the functionality and their business model.\\
\textbf{Responsible person(s):} Research Group\\
\textbf{Goal(s) and expected Results:} Information about current systems, their feature set and user-interface\\

\subsubsection{Empirical Study ES1}
\label{sect:workplan:phase1:es1}
\textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
\textbf{Description:} Create questionary for users, to get information about their thoughts about the systems discovered in \ref{sect:workplan:phase1:lr1}. They should evaluate these results and discover issues with their user-interface and functionality and also mention their needs regarding these two aspects.\\
The users current situation regarding the usage or the willingness to use of current systems are also parts to work out. \\
\textbf{Responsible person(s):} Research Group, Alpha-User \\
\textbf{Goal(s) and expected Results:} Knowledge about the user needs.\\

@@

\subsubsection{Prototyping P1}
\label{sect:workplan:phase2:p1}
\textbf{Dependencies:} RF2 \ref{sect:workplan:phase1:rf2}\\
\textbf{Description:} Create first version of horizontal prototype by creating the user-interface. Every part of the system should be covered.\\
\textbf{Responsible person(s):} Dev Team\\
\textbf{Goal(s) and expected Results:} first version of prototype\\

\subsubsection{Evaluation and Redesign ER1}
\label{sect:workplan:phase2:er1}
\textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
\textbf{Description:} The Alpha-Users should evaluate the prototype (interface and interaction) and redesign it by taking care of their input. This step should be repeated several times until there is no more additional useful feedback from the user-group.\\
\textbf{Responsible person(s):} Research Group, Alpha-Users, Dev Team\\
\textbf{Goal(s) and expected Results:} Information about necessary changes and redesigned prototype (Version 0.5, Milestone M2)\\

\subsubsection{Prototyping P2}
\label{sect:workplan:phase2:p2}
\textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
\textbf{Description:} Extend the existing prototype by adding functionality and implement the features.\\
\textbf{Responsible person(s):} Dev Team\\
\textbf{Goal(s) and expected Results:} Prototype with all features\\

\pagebreak
\subsubsection{Evaluierung und Redesign ER2}
\label{sect:workplan:phase2:er2}
\textbf{Dependencies:} P2 \ref{sect:workplan:phase2:p2}, ER2 \ref{sect:workplan:phase2:er2}\\
\textbf{Description:} The new prototype should be reevaluated by the Alpha-Users and also from the Dev Team (including Security and Quality Specialists). This step covers not only the interface and interaction, but also the quality and security of the product. The knowledge should be used to redesign the prototype and this step should be repeated several times. After a number of iterations the status of the web application should be switched to Beta and Beta-Users will be able to sign in and use the systems. After the last iteration the status should be switched to Release.\\
\textbf{Responsible person(s):} Alpha-Users, Beta-Users, Strategy Team, Dev Team\\
\textbf{Goal(s) and expected Results:} Released web application (Milestone M3)\\

@@

\subsubsection{Empirical Studie ES3}
\label{sect:workplan:phase3:es3}
\textbf{Dependencies:} LR2 \ref{sect:workplan:phase3:lr2}\\
\textbf{Description:} Establish user needs regarding an mobile app and get information about expectations of such an app \\
\textbf{Responsible person(s):} Research Team, Users\\
\textbf{Goal(s) and expected Results:} User needs regarding an mobile app\\

@@

\subsubsection{Prototyping P3}
\label{sect:workplan:phase3:p3}
\textbf{Dependencies:} ES3 \ref{sect:workplan:phase3:es3}\\
\textbf{Description:} Implement mobile version of the system with prototyping\\
\textbf{Responsible person(s):} Dev Team\\
\textbf{Goal(s) and expected Results:} Mobile clients\\

\subsubsection{Empirical Studie ES4}
\label{sect:workplan:phase3:es4}
\textbf{Dependencies:} None\\
\textbf{Description:} Establish if and which social health communities (e.g. tracking platforms) our users are using and find out how to integrate these partner into the system. \\
\textbf{Responsible person(s):} Research Team, Users\\
\textbf{Goal(s) and expected Results:} Possible new partners (3rd party services)\\
